### 2010-06-21 subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: docs

An active display client is needed when the component wants to present some UI
elements with which it can be configured. The client receives notifications and
requests related to these elements from the display server. The component must
define two callback functions that will handle the events sent by the server.

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   class VideoViewer : public ManagedComponent, public VideoClient
   {
   private:
   #ifdef FEAT_VISUALIZATION
     cogx::display::CActiveDisplayClient<VideoViewer> m_display;
     void handleGuiEvent(const Visualization::TEvent &event);
     std::string getControlState(const std::string& ctrlId);
   #endif
   };
\end{Verbatim}

The event path from the server to the client must be initiated. This is done right
after the component connects to the client. After the connections are established,
the callback functions are registered:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   void VideoViewer::start()
   {
   #ifdef FEAT_VISUALIZATION
     m_display.connectIceClient(*this);
     m_display.installEventReceiver();
     m_display.setEventCallback(this, &VideoViewer::handleGuiEvent);
     m_display.setStateQueryCallback(this, &VideoViewer::getControlState);
   #endif
   }
\end{Verbatim}

@@

The \code{handleGuiEvent()} callback function will be called every time the
UI element emits a known event. For the chekcbox element we need to respond
to the \code{evCheckBoxChange} event:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   #ifdef FEAT_VISUALIZATION
   void VideoViewer::handleGuiEvent(const Visualization::TEvent &event)
   {
     if (event.type == Visualization::evCheckBoxChange) {
       if (event.sourceId == "toggle.viewer.running") {
         bool newrcv = (event.data != "0");
         if (newrcv != receiving) {
           if(receiving) {
             videoServer->stopReceiveImages(getComponentID());
           }
           else {
             videoServer->startReceiveImages(getComponentID(), camIds, 0, 0);
           }
           receiving = !receiving;
         }
       }
     }
   }
   #endif
\end{Verbatim}

>>>>

An active display client is needed when the component wants to present some UI
elements with which it can be configured. The client receives notifications and
requests related to these elements from the display server. To achieve this 
a few methods must be overridden in a class derived from the CDisplayClient:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   class VideoViewer : public ManagedComponent, public VideoClient
   {
   private:
   #ifdef FEAT_VISUALIZATION
     class CVvDisplayClient: public cogx::display::CDisplayClient
     {
       VideoViewer* pViewer;
     public:
       CVvDisplayClient() { pViewer = NULL; }
       void setClientData(VideoViewer* pVideoViewer) { pViewer = pVideoViewer; }
       void handleEvent(const Visualization::TEvent &event); /*override*/
       std::string getControlState(const std::string& ctrlId); /*override*/
     };
     cogx::display::CActiveDisplayClient<VideoViewer> m_display;
   #endif
   };
\end{Verbatim}

In the constructor of the VideoViewer we call \code{setClientData()} so that
the new display client will be able to access the VideoViewer:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
  VideoViewer() : camId(0)
  {
#ifdef FEAT_VISUALIZATION
    m_display.setClientData(this);
#endif
  }
\end{Verbatim}

The event path from the server to the client must be initialized. This is done
right after the component connects to the client:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   void VideoViewer::start()
   {
   #ifdef FEAT_VISUALIZATION
     m_display.connectIceClient(*this);
     m_display.installEventReceiver();
   #endif
   }
\end{Verbatim}

@@

When the UI element is first displayed it has to obtain the current state from
the component that created it. This is done with the method
\code{getControlState()}:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   std::string VideoViewer::CVvDisplayClient::getControlState(
         const std::string& ctrlId)
   {
     if (ctrlId == "toggle.viewer.running") {
       return pViewer->receiving ? "1" : "0";
     }
     return "";
   }
\end{Verbatim}

The method \code{handleGuiEvent()} will be called every time the UI element
emits a known event. For the chekcbox element we need to respond to the
\code{evCheckBoxChange} event:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   #ifdef FEAT_VISUALIZATION
   void VideoViewer::CVvDisplayClient::handleGuiEvent(
         const Visualization::TEvent &event)
   {
     if (event.type == Visualization::evCheckBoxChange) {
       if (event.sourceId == "toggle.viewer.running") {
         bool newrcv = (event.data != "0");
         if (newrcv != receiving) {
           if(receiving) {
             videoServer->stopReceiveImages(getComponentID());
           }
           else {
             videoServer->startReceiveImages(getComponentID(), camIds, 0, 0);
           }
           receiving = !receiving;
         }
       }
     }
   }
   #endif
\end{Verbatim}
